---
title: '**Week 8: In Class Notes**'
author: "Yunjae"
date: "March 29, 2017"
output: html_document
---

## Yunjae Choi

<!-- leave this material as is -->
Compiled on `r date()`.
```{r include = FALSE}
library(DataComputing)
library(ggplot2)
library(statisticalModeling)
library(rpart)
library(randomForest)
library(stats4)
library(cluster)
```
<!-- put your content after this line -->


&nbsp;
&nbsp;

##### this is a made up data called `Carseats` 

```{r}
# require(ISLR)
data(Carseats, package = "ISLR")
?Carseats
```

##### unit of observation: store (depending on the time period)

&nbsp;

# **Variables that Seem Important: Formulate an Interesting Question**

### **_Example Graph_**
```{r}
graphic_format <- 
  ggplot(data = Carseats, aes(x = Price, y = Sales, color = Urban)) +
  geom_point() +
  ggtitle("Price vs. Sales") +
  xlab("Price") + 
  ylab("Sales")
graphic_format
```


### **_`lm` and `anova`_**
```{r}
## sequential table
fit <- lm(sr ~ ., data = LifeCycleSavings)
anova(fit)

## same effect via separate models
fit0 <- lm(sr ~ 1, data = LifeCycleSavings)
fit0
fit1 <- update(fit0, . ~ . + pop15)
fit1
fit2 <- update(fit1, . ~ . + pop75)
fit2
fit3 <- update(fit2, . ~ . + dpi)
fit3
fit4 <- update(fit3, . ~ . + ddpi)
fit4
```

&nbsp;

### **_F test for `anova`_**
```{r}
anova(fit0, fit1, fit2, fit3, fit4, test = "F") # F test
anova(fit4, fit2, fit0, test = "F") # unconventional order
```

&nbsp;

### **_Our Example Using `anova`_**
```{r}
model_1 <- Sales ~ Price + Population + CompPrice
linear <- lm(model_1, data = Carseats)
anova <- anova(linear)
anova
```

&nbsp;

### **_Random Forest_**
https://cran.r-project.org/web/packages/randomForest/randomForest.pdf
```{r}
data(iris)
head(iris)
iris.rf <- randomForest(iris[,-5], iris[,5], prox=TRUE)
iris.p <- classCenter(iris[,-5], iris[,5], iris.rf$prox)
plot(iris[,3], iris[,4], pch=21, xlab=names(iris)[3], ylab=names(iris)[4],
bg=c("red", "blue", "green")[as.numeric(factor(iris$Species))],
main="Iris Data with Prototypes")
points(iris.p[,3], iris.p[,4], pch=21, cex=2, bg=c("red", "blue", "green"))
```

```{r}
data(iris)
rf1 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
rf2 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
rf3 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
rf.all <- combine(rf1, rf2, rf3)
print(rf.all)
```

&nbsp;

### **_Maximum Likelihood Estimate_**
https://stat.ethz.ch/R-manual/R-devel/library/stats4/html/mle.html
```{r}
## Avoid printing to unwarranted accuracy
od <- options(digits = 5)
x <- 0:10
y <- c(26, 17, 13, 12, 20, 5, 9, 8, 5, 4, 8)

## Easy one-dimensional MLE:
nLL <- function(lambda) -sum(stats::dpois(y, lambda, log = TRUE))
fit0 <- mle(nLL, start = list(lambda = 5), nobs = NROW(y))
# For 1D, this is preferable:
fit1 <- mle(nLL, start = list(lambda = 5), nobs = NROW(y),
            method = "Brent", lower = 1, upper = 20)
stopifnot(nobs(fit0) == length(y))

## This needs a constrained parameter space: most methods will accept NA
ll <- function(ymax = 15, xhalf = 6) {
    if(ymax > 0 && xhalf > 0)
      -sum(stats::dpois(y, lambda = ymax/(1+x/xhalf), log = TRUE))
    else NA
}
(fit <- mle(ll, nobs = length(y)))
mle(ll, fixed = list(xhalf = 6))
## alternative using bounds on optimization
ll2 <- function(ymax = 15, xhalf = 6)
    -sum(stats::dpois(y, lambda = ymax/(1+x/xhalf), log = TRUE))
mle(ll2, method = "L-BFGS-B", lower = rep(0, 2))

AIC(fit)
BIC(fit)

summary(fit)
logLik(fit)
vcov(fit)
plot(profile(fit), absVal = FALSE)
confint(fit)

## Use bounded optimization
## The lower bounds are really > 0,
## but we use >=0 to stress-test profiling
(fit2 <- mle(ll, method = "L-BFGS-B", lower = c(0, 0)))
plot(profile(fit2), absVal = FALSE)

## a better parametrization:
ll3 <- function(lymax = log(15), lxhalf = log(6))
    -sum(stats::dpois(y, lambda = exp(lymax)/(1+x/exp(lxhalf)), log = TRUE))
(fit3 <- mle(ll3))
plot(profile(fit3), absVal = FALSE)
exp(confint(fit3))

options(od)
```



### **_Hierarchical Clustering_**
https://cran.r-project.org/web/packages/cluster/cluster.pdf

```{r}
data(votes.repub)
agn1 <- agnes(votes.repub, metric = "manhattan", stand = TRUE)
agn1
plot(agn1)
op <- par(mfrow=c(2,2))
agn2 <- agnes(daisy(votes.repub), diss = TRUE, method = "complete")
plot(agn2)
## alpha = 0.625 ==> beta = -1/4 is "recommended" by some
agnS <- agnes(votes.repub, method = "flexible", par.meth = 0.625)
plot(agnS)
par(op)
## "show" equivalence of three "flexible" special cases
d.vr <- daisy(votes.repub)
a.wgt <- agnes(d.vr, method = "weighted")
a.sing <- agnes(d.vr, method = "single")
a.comp <- agnes(d.vr, method = "complete")
iC <- -(6:7) # not using 'call' and 'method' for comparisons
stopifnot(
all.equal(a.wgt [iC], agnes(d.vr, method="flexible", par.method = 0.5)[iC]) ,
all.equal(a.sing[iC], agnes(d.vr, method="flex", par.method= c(.5,.5,0, -.5))[iC]),
all.equal(a.comp[iC], agnes(d.vr, method="flex", par.method= c(.5,.5,0, +.5))[iC]))
## Exploring the dendrogram structure
(d2 <- as.dendrogram(agn2)) # two main branches
d2[[1]] # the first branch
d2[[2]] # the 2nd one { 8 + 42 = 50 }
d2[[1]][[1]]# first sub-branch of branch 1 .. and shorter form
identical(d2[[c(1,1)]],
d2[[1]][[1]])
## a "textual picture" of the dendrogram :
str(d2)
data(agriculture)
## Plot similar to Figure 7 in ref
## Not run: plot(agnes(agriculture), ask = TRUE)
data(animals)
aa.a <- agnes(animals) # default method = "average"
aa.ga <- agnes(animals, method = "gaverage")
op <- par(mfcol=1:2, mgp=c(1.5, 0.6, 0), mar=c(.1+ c(4,3,2,1)),
cex.main=0.8)
plot(aa.a, which.plot = 2)
plot(aa.ga, which.plot = 2)
par(op)
## Show how "gaverage" is a "generalized average":
aa.ga.0 <- agnes(animals, method = "gaverage", par.method = 0)
stopifnot(all.equal(aa.ga.0[iC], aa.a[iC]))
```



```{r}
data(agriculture)
ag.ag <- agnes(agriculture)
class(ag.ag)
pltree(ag.ag) # the dendrogram
## cut the dendrogram -> get cluster assignments:
(ck3 <- cutree(ag.ag, k = 3))
(ch6 <- cutree(as.hclust(ag.ag), h = 6))
stopifnot(identical(unname(ch6), ck3))
```
