# Week 3 Project

## Your name should appear here! 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->


Considering each of the above graphics in turn, figure out:



* What mode of graphic is it? (e.g. density plot, scatter plot, bar plot, …)

  density plot


* What variables from the respective data tables are involved?

  bmi, sex, pregnancy (yes/ no)


* What role each of those variables plays in the graphic?

  pregnancy - divided into two layers
  sex - using color codes (aesthetics)
  density plot of bmi depending on sex and preg
  
  
* In Figure 2, why is there no data variable being used for the yy-axis?

  same as the one in the left
  


```{r}
library(mosaicData)
library(ggplot2)
# View(CPS85)
View(NCHS)
fit <-lm(wage ~ height, data=women)
ggplot(data = CPS85, aes(x = exper, y = wage, color = "red")) + geom_point() + facet_wrap( ~ sex)
                                                                        
ggplot(data = NCHS, aes(x = weight)) + geom_density(aes(color = "red")) + facet_wrap(~ sex)
```

### Just a practice
```{r}
diamonds %>% 
  group_by( color , clarity ) %>% 
  summarise( price = mean(price), ncases = n()) %>% 
  arrange(desc( price )) %>% 
  head( 1 )
```

### 1.

Which color diamonds seem to be largest on average (in terms of carats)?

J

```{r}
diamonds %>% 
  group_by( color ) %>% 
  summarise(nmean = mean(carat)) %>%
  arrange(desc(nmean)) %>% 
  head( 10 )
```



Which clarity of diamonds has the largest average “table” per carat?

Il

```{r}
diamonds %>% 
  group_by( clarity ) %>% 
  summarise(nmean = mean(table)) %>%
  arrange(desc(nmean)) %>% 
  head( 10 )
```


## Voting

How many cases are there?

```{r}
View(Minneapolis2013)
Minneapolis2013 %>% 
  summarise(nsum = n())
```


Who were the top 5 candidates in the Second vote selections?

!!!
```{r}
Minneapolis2013 %>% 
  group_by(Second) %>%
  summarise(nsum = n()) %>%
  arrange(desc(nsum)) %>% 
  head( 5 )
```



How many ballots are marked “undervote” in First choice selections?
Second choice selections?
Third choice selections?

tally vs. count

```{r}
Minneapolis2013 %>% 
  filter(First == "undervote") %>%
  summarise(nsum = n())
```


```{r}
Minneapolis2013 %>% 
  filter(Second == "undervote") %>%
  summarise(nsum = n())
```


```{r}
Minneapolis2013 %>% 
  filter(Third == "undervote") %>%
  summarise(nsum = n())
```




What are the top 3 Second vote selections among people who voted for Betsy Hodges as their first choice?

```{r}
Minneapolis2013 %>% 
  filter(First == "BETSY HODGES") %>%
  group_by(Second) %>%
  summarise(nsum = n()) %>%
  arrange(desc(nsum)) %>%
  head(3)
```






Which Precinct had the highest fraction of First vote selections marked as “undervote”? (To calculate the fraction, use mean(First == "undervote") in the argument to summarise().)

```{r}
Minneapolis2013 %>% 
  group_by(Precinct) %>% 
  summarise(frac = mean(First == "undervote")) %>%
  arrange(desc(frac)) %>%
  head(1)
```










