# **Week 3 Short Answer Questions**

## Yunjae Choi

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

&nbsp;    
&nbsp;    

### Chapter 5
    
##### Problem 5.1
```{r}
ggplot(data=CPS85,
       aes(x=sex, y=wage, fill=married)) + 
  geom_bar(stat='identity', position='dodge', width=.9) + 
  facet_wrap(~race, ncol=3)
```

##### Problem 5.2
```{r}
HappinessIndex %>%
WorldMap(key="country", fill="corruption")
```

&nbsp;    
&nbsp;    

### Chapter 6

##### Problem 6.5    

    b

##### Problem 6.6      

    d

##### Problem 6.7    

    c

##### Problem 6.8
```{r}
Small <-
NCHS %>%
  sample_n(size=5000)
Small <- na.omit(Small)
Small$smoker <- factor(Small$smoker,labels=c("no","yes"))
ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker)
```

&nbsp;    
&nbsp;    

### Chapter 7

##### Problem 7.1

a. Find the average of one of the variables.

        summarise() 

b. Add a new column that is the ratio between two variables.

        mutate() 

c. Sort the cases in descending order of a variable.

        arrange() 

d. Create a new data table that includes only those cases that meet a criterion.

        filter() 

e. Form a data table with three categorical variables A, B, & C, and a quantitative variable X, produce an output that has the same cases but only the variables A and X.

        select() 


f. From a data table with three categorical variables A, B, & C, and a quantitative variable X, produce an output that has a separate case for each of the combinations of the levels of A and B. (Hint: It might be easier to see the answer if the problem statement added, “and gives the maximum value of X over all the cases that have a given combination of A and B.” )

        group_by() and summarise()

&nbsp;

##### Problem 7.4

a. What's Wrong:    
        
        Quotation marks around "First"; it's a variable and the data is from Minneapolis2013
    
    Should Be:    
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(votesReceived = n())
```

&nbsp;

b. What's Wrong:

        Cannot have the assigned object name as the argument inside a function

    Should Be: 
```{r}
Tmp <- group_by(BabyNames, year, sex) %>%
  summarise(totalBirths = sum(count))
Tmp
```

&nbsp;

c. What's Wrong:

        Cannot repeat data set

    Should Be:
```{r}
Tmp <- group_by(BabyNames, year, sex) %>%
  summarise(totalBirths = sum(count))
Tmp
```

&nbsp;

##### Problem 7.5

a.
```{r}
tablea <- BabyNames %>%
  arrange (sex, count) %>%
  head(6)
tablea
```

b.
```{r}
tableb <- BabyNames %>%
  filter(sex == "F") %>%
  head(6)
tableb
```

c.
```{r}
tablec <- BabyNames %>%
  filter(sex == "M", count > 10) %>%
  head(6)
tablec
```

d.
```{r}
tabled <- BabyNames %>%
  summarise( total= sum(count) ) %>%
  head(6)
tabled
```

e. 
```{r}
tablee <- BabyNames %>%
  select(name, count) %>%
  head(6)
tablee
```

&nbsp;

##### Problem 7.7

a. BabyNames is used twice.

    Should Be:
```{r}
BabyNames %>% 
group_by(year, sex) %>%
summarise(total = sum(count))
```

&nbsp;

b. ZipGeography is a dataset, not an assignment name. There's no data referring to this object.

    Should Be:
```{r}
ZipGeography %>%
  group_by(State) %>%
  summarise(pop = sum(Population))
```

&nbsp;

c. assignment symbol used instead of a chaining syntax

    Should Be:
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(voteReceived = n())
```

&nbsp;

d. all order backward AND ">" should be used, not "<"

    Should Be:
```{r}
Minneapolis2013 %>% group_by(First) %>% summarise(votesReceived = n())
```

&nbsp;

##### Problem 7.11

a. column headings will look like: 

    1. two levels of sex
    2. total counts for each sex
    3. mean age of each group (sex)    
    
&nbsp;

b. column headings will look like:  

    1. All levels of diagnosis
    2. total counts for each level of diagnosis
    3. mean age of each level of diagnosis    
    
&nbsp;

c. column headings will look like: 

    1. the first two: two levels of sex, each divided by the levels of diagnosis
    2. total counts of each group (sex) subdivided by diagnosis
    3. mean age of for each group (sex) subdivided by diagnosis    
    
&nbsp;

d. column headings will look like:  

    1. the first two: all levels of age, each divided by the levels of diagnosis
    2. total counts of each age subdivided by diagnosis
    3. mean age of for each age subdivided by diagnosis    
    
&nbsp;

e. column headings will look like: 

    1. age
    2. total counts for each age
    3. mean age of the first column's age which is the same as age
    
&nbsp;

##### Problem 7.12

1. Count the number of cases in a data table.

        nrow()


2. List the names of the variables in a data table.

        variable.names(data)
        OR
        names()

3. For data tables in an R package, display the documentation (“codebook”) for the data table.

        help(data)


4. Load a package into your R session.

        library(package)


5. Mark a data table as grouped by one or more categorical variables.    

        group_by()


6. Add up, group-by-group, a quantitative variable in a data table.

        summarise( quantVarHeading = sum(quantvar))







