# **Week 5 Project**

## Yunjae Choi


<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(dplyr)
library(tidyr)
```
<!-- put your content after this line -->

&nbsp;

https://dtkaplan.github.io/comp110/Projects/552-Economist-graph.html
##### _Downloading Data_
```{r eval = FALSE}
download.file("http://tiny.cc/dcf/ScorecardSmall.csv", 
              destfile = "ScorecardSmall.csv")
```

```{r cache=TRUE}
ScorecardSmall <- read.csv("ScorecardSmall.csv", stringsAsFactors = FALSE)
```

&nbsp;

##### _Wrangling Data_
###### `gather()`

* `gather` takes multiple columns and collapses into key-value pairs, duplicating all other columns as needed. You use `gather` when you notice that you have columns that are not variables.

        gather(data, key, value, ...)
        
* `substr` replaces substrings in a character vector  

        substr(x, start, stop)

```{r}
ScorecardSmall %>%
  select(CCSIZSET, CONTROL, ADM_RATE, NPT41_PUB, NPT41_PRIV, NPT43_PRIV,NPT43_PUB, NPT45_PRIV, NPT45_PUB) %>%
  filter(CONTROL!=3) %>%
  tidyr::gather(key = Quantile, value = Cost, NPT41_PUB, NPT41_PRIV, NPT43_PRIV,NPT43_PUB, NPT45_PRIV, NPT45_PUB) %>%
  mutate(Q = substr(Quantile, 5,5)) %>%
  head()
```

&nbsp;


##### **_Chunk Codes_**
```{r warning = FALSE}

ScorecardSmall %>%
  mutate(CONTROL = ifelse(CONTROL == 1, "PUBLIC", "PRIVATE")) %>%
  select(CCSIZSET, CONTROL, ADM_RATE, NPT41_PUB, NPT41_PRIV, NPT43_PRIV,NPT43_PUB, NPT45_PRIV, NPT45_PUB) %>%
  filter(CONTROL!=3) %>%
  tidyr::gather(key = Quantile, value = Cost, NPT41_PUB, NPT41_PRIV, NPT43_PRIV,NPT43_PUB, NPT45_PRIV, NPT45_PUB) %>%
  mutate(Q = substr(Quantile, 5,5)) %>%
  mutate(Q = paste0("Q", Q)) %>%
  ggplot(aes(x = ADM_RATE, y = Cost)) + 
  geom_point(color = "blue", alpha = 0.05) + 
  facet_grid(CONTROL ~ Q) + 
  geom_smooth(color="black") + xlab("Admission Rate") + ylab("Cost")
```




##### **_Reference Using `Factor`_**
```{r}
data <- transform(mtcars,
  am = factor(am, levels = 0:1, c("Automatic", "Manual")),
  gear = factor(gear, levels = 3:5, labels = c("Three", "Four", "Five"))
)
p <- ggplot(data, aes(mpg, disp)) + geom_point()
p + facet_grid(am ~ gear, switch = "both")
# It looks better without boxes around the strips
p + facet_grid(am ~ gear, switch = "both") +
  theme(strip.background = element_blank())
```





