---
title: "**Week 4: In Class Notes**"
author: "Yunjae"
date: "March 14, 2017"
output: html_document
---

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

&nbsp;

### In-Class Notes

```{r}
data(WorldCities, package = "DataComputing")
select <- WorldCities %>% 
  select(name)
```

&nbsp;

#### Some Data Verbs

select()
```{r}
select <- WorldCities %>% 
  select(name)
```

mutate()
```{r}
m <- WorldCities %>% 
  mutate(spop = sqrt(population))
```

select() + mutate()
```{r}
ms <- WorldCities %>%
  mutate(spop = sqrt(population)) %>% 
  select(name)
```

transmute()
```{r}
WorldCities %>% 
  transmute(spop = sqrt(population)) -> transm
```

grepl()
```{r}
vowel <- BabyNames %>% 
  mutate(with_vowel = grepl("^[AEIOU]", name))
```

Example) vowel12
```{r}
vowel2 <- vowel %>% 
  group_by(year) %>%
  summarise(total_w_vowel = sum(with_vowel), total_names = n()) %>% 
  mutate(fraction = total_w_vowel / total_names) %>% 
  select(year, fraction)
```

&nbsp;

### Data Wrangling Vocabulary

1. Target table
1. Two questions to ask

    + Are the cases different?
    + Are the variables different?

&nbsp;

### Functions of Functions

1. Data Verb takes as an input a data table -> data table
1. Reduction Verbs takes as an input variable -> number
1. Transformation Verb takes as an input variable -> variable

    + Rank Transformations: "find the largest...", "Find the three largest", "Find the smallest within each group"
    + Lead and lag transformations
    + Times and Dates: transform text dates into an R type with numerical properties
    + Lead and lag transformations
    + Lead and lag transformations
