# **Week 6 Short Answer Questions**

## Yunjae Choi

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(tidyr)
library(ggplot2)
```
<!-- put your content after this line -->

&nbsp;    
&nbsp;    

### Chapter 12
    
##### Problem 12.1
For each sex, find the 5 most popular names in BabyNames adding up over all the years.
```{r}
BabyNames_ranks <- BabyNames %>%
  group_by(sex, name) %>%
  summarise(nNames = sum(count)) %>%
  mutate(rank = rank(desc(nNames))) %>% 
  filter(rank <= 5) %>% 
  arrange(desc(rank))

BabyNames_ranks
```

##### For Myself: Steps
```{r}
# PopularCounts <-
#   BabyNames %>%
#   group_by(year, name) %>% 
#   summarise(total = sum(count)) %>%
#   mutate(ranking = ifelse(rank(desc(total)) <= 100, "Top_100", "Below"))
# PopularCounts
```



&nbsp;    

##### Problem 12.2

```{r}
PopularCounts <-
  BabyNames %>%
  group_by(year, name) %>%
  summarise(total = sum(count)) %>%
  mutate(ranking = ifelse(rank(desc(total)) <= 100, "Top_100", "Below")) %>%
  group_by(year, ranking) %>%
  summarise(total = sum(total))

##### For Myself: Steps
# GlyphReady <-
#   PopularCounts %>%
#   tidyr::spread(ranking, total)
# GlyphReady

GlyphReady <-
  PopularCounts %>%
  spread(ranking, total) %>%
  mutate(frac_in_top_100 = Top_100 / (Top_100 + Below))

GlyphReady %>%
  ggplot(aes(x=year, y=frac_in_top_100)) +
  geom_line() +
  ylim(0, NA)
```

&nbsp;    

##### Problem 12.3

a. summary
b. neither a summary nor a transformation. It is a pair of values rather than a single value as required for a summary function.
c. summary
d. transf
e. transf
f. summary
g. transf
h. summary. an entire set of dates is being
turned into a single number.


&nbsp;    
&nbsp;    

### Chapter 13

##### Problem 13.1

1. There are 7 distinct vertices: China, France, Germany, Italy, UK, USA, USSR
2. There is one row for each edge, so 9 edges.


&nbsp;    

##### Problem 13.2

1. A,B,C,D
2. table 2
3. bc not paired
4. no three pairs (only 2)

&nbsp;    

##### Problem 13.3

NA

&nbsp;    

##### Problem 13.4

1. exports
2. pop

&nbsp;    
&nbsp;    

### Chapter 14

##### Problem 14.1

```{r warning = FALSE}
mosaicData::CPS85 %>%
ggplot(aes(x = sex, y = wage)) +
geom_boxplot(aes(fill=sex))

# data(CPS85, package = "mosaicData")
# names(CPS85)
# ggplot(CPS85, aes(x = sex, y = wage)) +
#   geom_boxplot(aes(color = sex)) 
```


&nbsp;    

##### Problem 14.3

For women, a litle less than 1.60 meters. For men, about 1.75 meters.

&nbsp;    

##### Problem 14.7

```{r warning = FALSE}
mosaicData::CPS85 %>%
  ggplot(aes(x = educ, y = wage, color = sex)) +
  geom_point() +
  stat_smooth(method="lm") +
  ylim(0,15)
```


&nbsp;    

##### Problem 14.10

```{r warning = FALSE}
mosaicData::Galton %>%
  ggplot(aes(x = height)) +
  geom_density(aes(fill = sex, color = sex), alpha = 0.5) +
  ggtitle("Height based on Gender") 
```

