---
title: "Week-6-in-class-activity-notes"
author: "Yunjae"
date: "March 29, 2017"
output: html_document
---
# **Week 6 Project**

## Yunjae Choi

# WARNING: individual project; put away for later

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(dplyr)
library(igraph)
library(tidyr)
library(stats)
library(base)
library(ggplot2)
library(mosaic)
download.file("http://tiny.cc/dcf/MovieLens.rda", 
              destfile = "MovieLens.rda")
```
<!-- put your content after this line -->

&nbsp;

##### _Loading Data_
```{r}
load("~/Comp-110-Assignments-Spring-2017/Data Sets/MovieLens.rda")
```

&nbsp;

##### **_`MovieLens.rda` contains three data tables:_**

* `Ratings` has the individual movie ratings and the time at which they were entered. It also includes an ID variable for both the user and the movie. 
* `Movies` provides the name of the movie and information about genres. 
* `Users` gives basic information about the person who made the rating.

**Your task: Construct each of these graphics.**

&nbsp;

#### **_`Ratings` and `Users` Joined by `user_id`_**
```{r}
All <- left_join(Ratings, Users, by = "user_id")
```

#### **_`Ratings`, `Users`, `Movies` Joined by `user_id`and 'movie_id'_**
```{r}
All <- left_join(All, Movies, by = "movie_id")
All
```


#### **_`Ratings` and `Users` Joined by `user_id`_**

!!! Variable names like Film-Noir, Sci-Fi and Children's do not work
!!! also don't know if this is necessary

Movies[,6:23]

```{r}
names(Movies)
# Genresmod <- 
#   Movies %>%
# #  select(movie_id, Movies[,6:23]) %>%
#   gather(key = genre, value = bool, Movies[,6:23])
# 
# Genresmod
```


```{r}
names(Movies)
Genresmod <- 
  Movies %>%
#  select(movie_id, Movies[6:23]) %>%
  gather(key = genre, value = bool, Action, Adventure, Animation, Comedy, Crime,Documentary, Drama, Fantasy, Horror, Musical, Mystery, Romance, Thriller, War, Western)

Genresmod
```

&nbsp;

### _Show the appeal of different genres to the different sexes_

```{r}
Result %>% 
  ggplot(aes(x = year, y = count, color = name)) +
  geom_point() +
  ggtitle("Yearly Number of Janes and Mary") +
  xlab("Year") + 
  ylab("Count")
```

!!! how to make the genre variable fit into the graph
```{r}
names(All)
All %>% ggplot(aes(x = mean(rating), y = genre, color = sex)) +
         geom_errorbar() 
```

&nbsp;

### _Which genres are related?_

!!! where did first and second come from?
```{r}
co_occurance <- function(genres){
  f <- function(x,y) {sum(x * y) / sum(x)}
  M <- matrix(0, nrow = ncol(genres), ncol = ncol(genres))
  for (first in 1:ncol(genres)) {
    for (second in 1:ncol(genres)) {
      M[first, second] <- f(genres[[first]], genres[[second]])
    }
  }
  M <- as.data.frame(M)
  names(M) <- names(genres)
  M$genre <- names(genres)
  M %>%
    tidyr::gather(key = genre2, value = co_occur, -genre)
}
```

```{r}
Genres <- Movies[,6:23]
```

```{r}
tmp <- cor(Genres) %>% as.data.frame(stringsAsFactors = FALSE)
```

```{r}
tmp$genre <- row.names(tmp)
```

```{r}
Genre_pairs <-
  tmp %>% 
  gather(key = genre2, value = correlation, -genre) %>%
  filter(genre != genre2) %>%
  group_by(genre) %>%
  mutate(cor_sign = as.character(sign(correlation))) %>%
  mutate(cor_size = abs(correlation))
```

```{r}
Genre_co_occur <- co_occurance(Genres) %>%
  filter(genre != genre2)
```


```{r}
Genre_pairs %>%
  ggplot(aes(x = genre2, y = genre)) + 
  geom_point(aes(size = cor_size, color = cor_sign)) +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5))
```


```{r}
Genre_co_occur %>%
  ggplot(aes(x = genre2, y = genre)) +
  geom_point(aes(size = co_occur)) +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5))
```

##### As a network
```{r}
Keep_pairs <- 
  Genre_pairs %>%
  filter(cor_size > 0.05, cor_sign == "1") %>%
  filter(genre > genre2) 
```

```{r}
Vertices <- Keep_pairs %>% 
  edgesToVertices(from = genre, to = genre2) 
```

```{r}
Edges <- 
  Vertices %>%
  edgesForPlotting(ID = ID, x, y, Edges = Keep_pairs, from = genre, to = genre2)
```

```{r}
Vertices %>%
  ggplot(aes(x = x, y = y)) + geom_point()+
  geom_segment(data = Edges, 
               aes(x = x, y = y, xend = xend, yend = yend, 
                   color = correlation, size = correlation)) + 
  theme_map() + 
    geom_label(aes(label = ID), fill = "white") 
```

&nbsp;

### _Who are the reviewers?_
```{r}
Users %>%
  ggplot(aes(x = age)) + 
  geom_density(aes(fill = occupation), 
               color = NA, alpha = .7, position = "fill") + 
  facet_wrap( ~ sex)
```

```{r}
Users %>%
  ggplot(aes(x = age)) + 
  geom_density(aes(fill = sex), 
               color = NA, alpha = .4, position = "fill")
```

```{r}
Users %>%
  group_by(occupation) %>%
  tally() %>%
  arrange(desc(n))
```

&nbsp;

### _Ratings as people age_
!!! genre not found
```{r}
All %>%
  filter( genre != "unknown") %>%
  ggplot(aes(x = age, color = sex, y = rating)) + 
  geom_smooth() + 
  facet_wrap( ~ genre, scales = "free")
## `geom_smooth()` using method = 'gam'
```

```{r}
All %>% 
  ggplot(aes(x = age, color = sex, y = rating)) +
  geom_smooth()
## `geom_smooth()` using method = 'gam'
```