# **Week 7 Short Answer Questions**

## Yunjae Choi

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(xml2)
library(bitops)
library(rvest)
library(RCurl)
```
<!-- put your content after this line -->


&nbsp;    
&nbsp; 

### Chapter 15
    
##### Problem 15.1

• "April 30, 1777" — mdy()
• "06-23-1912" — mdy()
• "3 March 1847" — dmy()
• "11:00 am on Nov. 11th, 1918 at 11:00 am" —
mdy_hm()
• "July 20, 1969" — mdy()

```{r}
lubridate::ymd("1941-09-01") -
lubridate::mdy("July 28th, 1914")
lubridate::ymd("1941-09-01")
```


&nbsp; 

##### Problem 15.2

a. "42,659.30" - tidyr::extract_numeric()
b. "17%" - tidyr::extract_numeric()
c. "Nineteen" - as_numeric()
d. "£100" - tidyr::extract_numeric()
e. "9.8 m/seconds-square" - as_numeric()
f. "9.8 m/sˆ2" - as_numeric()
g. "6.62606957 × 10ˆ-34 m2 kg / s" - as_numeric()
h. "6.62606957e-34" - as_numeric()
i. "42.659,30" (A European style)  - tidyr::extract_numeric()


&nbsp; 


### Chapter 16


##### Problem 16.1

1) Boys’ names ending in a vowel.

```{r}
BabyNames %>%
  # Filter to keep only the boys.
  filter(sex == "M") %>%
  # Add up across all years for each name
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  # Filter to find names ending in a vowel
  # The $ is the end-of-string marker
  filter(grepl("[aeiou]$", name)) %>%
  # Grab the top 10.
  arrange(desc(total)) %>%
  head(10)
```


2. Names ending with "joe" or "jo"

```{r}
BabyNames %>%
  # Add up across all years for each name
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  # Filter to find names ending in [jo|joe]
  # The $ is the end-of-string marker
  filter(grepl(".*(jo$|joe$)", name)) %>%
  # Grab the top 10.
  arrange(desc(total)) #%>%
  head(10)
```



&nbsp; 

##### Problem 16.2

Here is a character string with a regular expression:
"([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"

It's a structure of a US phone number. It starts with a number between 2 and 9 followed by two numbers in the set {0, ... , 9}. It then links to three numbers from the same number set {0, ... , 9}, has a link again, and ends with four numbers in the set {0, ... , 9}.



&nbsp; 

##### Problem 16.3

1. Each matched string will be two letters, e.g. AL, AK, AS.
2. For a pattern like A[LKSZRAP], there are seven strings
that match. For an pattern like D[EC], there are two
strings that match: DE and DC. For a pattern like RI,
there is only one string that matches. Altogether, 61
patterns.
3. These are abbreviations for the US states and territories.















