# **Week 3 Project**

## Yunjae Choi

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

&nbsp;

#### The Basics

Considering each of the above graphics in turn, figure out:

* What mode of graphic is it? (e.g. density plot, scatter plot, bar plot, …)

        density plot  

&nbsp;
  
* What variables from the respective data tables are involved?  

        bmi, sex, pregnancy (yes/ no)  

&nbsp;
  
* What role each of those variables plays in the graphic?  

        pregnancy - divided into two layers
        sex - using color codes (aesthetics)
        density plot of bmi depending on sex and preg  
        
&nbsp;
  
* In Figure 2, why is there no data variable being used for the $y$-axis?  
    
        same as the one in the left  

&nbsp;
&nbsp;

#### Making Plots

```{r}
library(mosaicData)
library(ggplot2)
```


```{r}
ggplot(data = CPS85, aes(x = exper, y = wage, color = "red")) + geom_point() + facet_wrap( ~ sex)                  
ggplot(data = NCHS, aes(x = weight)) + geom_density(aes(color = "red")) + facet_wrap(~ sex)
```



#### Diamonds

1. Which color diamonds seem to be largest on average (in terms of carats)?  
        J is the largest on average

```{r}
diamonds %>% 
  group_by( color ) %>% 
  summarise(carat_size = mean(carat)) %>%
  arrange(desc(carat_size)) %>% 
  head( 10 )
```


2. Which clarity of diamonds has the largest average “table” per carat?  

        Il

```{r}
diamonds %>% 
  group_by( clarity ) %>% 
  summarise(nmean = mean(table)) %>%
  arrange(desc(nmean)) %>% 
  head( 10 )
```



#### Voting

How many cases are there?

```{r}
Minneapolis2013 %>% 
  summarise(nsum = n())
```


Who were the top 5 candidates in the Second vote selections?

```{r}
Minneapolis2013 %>% 
  group_by(Second) %>%
  summarise(nsum = n()) %>%
  arrange(desc(nsum)) %>% 
  head( 5 )
```




How many ballots are marked “undervote” in First choice selections?

```{r}
Minneapolis2013 %>% 
  filter(First == "undervote") %>%
  summarise(nsum = n())
```


Second choice selections?

```{r}
Minneapolis2013 %>% 
  filter(Second == "undervote") %>%
  summarise(nsum = n())
```


Third choice selections?

```{r}
Minneapolis2013 %>% 
  filter(Third == "undervote") %>%
  summarise(nsum = n())
```



What are the top 3 Second vote selections among people who voted for Betsy Hodges as their first choice?

```{r}
Minneapolis2013 %>% 
  filter(First == "BETSY HODGES") %>%
  group_by(Second) %>%
  summarise(nsum = n()) %>%
  arrange(desc(nsum)) %>%
  head(3)
```



Which Precinct had the highest fraction of First vote selections marked as “undervote”? (To calculate the fraction, use mean(First == "undervote") in the argument to summarise().)

```{r}
Minneapolis2013 %>% 
  group_by(Precinct) %>% 
  summarise(frac = mean(First == "undervote")) %>%
  arrange(desc(frac)) %>%
  head(1)
```










