---
title: '**Week 7: In Class Notes**'
author: "Yunjae Choi"
date: "March 15, 2017"
output: html_document
---


<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(dplyr)
library(base)
library(stringr)
```
<!-- put your content after this line -->

&nbsp;
&nbsp;

# Macbeth
```{r, include = FALSE}
macbeth_url <- "http://www.gutenberg.org/cache/epub/1129/pg1129.txt"
macbeth_raw <- RCurl::getURL(macbeth_url)     # grabs text from a url
```

### Text Inspection: How many characters in text
```{r}
class(macbeth_raw)
length(macbeth_raw)
nchar(macbeth_raw)      
```

```{r}
macbeth <- strsplit(macbeth_raw, "\r\n")[[1]]
macbeth[300:310]
```



The regular way of writing:

`"^  [A-Z]{2,}\\."`

`"^ {1,3}[A-Z]{2,}\\."`


* ^ = starting at the beginning of the string
*   = space
* [] = set
* {} = repeated at least two times and maybe more  
* . = anything
* //. = period taken literally (escape)
  


```{r}
pattern <- "^  [A-Z]{2,}\\."
macbeth_lines <- grep(pattern, macbeth, value = TRUE)
head(macbeth_lines)
tail(macbeth_lines)
```

  

```{r}
library(stringr)
pattern <- "^  [A-Z]{2,}\\."

characters <- 
  grep(pattern, macbeth, value = TRUE) %>%
  str_extract(pattern)

table(characters)
```

&nbsp;
&nbsp;


# BabyNames
```{r}
# data(BabyNames)
BabyNames %>% head()
BabyNames %>% sample_n(size = 20)
```

```{r}
BabyNames %>% sample_n(size = 10000) -> Names
```

### Names that begin with vowels

##### grepl = grep logical - boolean
```{r}
WithVowels <-
  Names %>%
  filter(grepl("^[AEIOUY]", name))
```


```{r}
WithVowels <-
  Names %>%
  group_by(sex) %>%
  summarise(total = sum(count))
```


```{r}
BabyNames <-
  Names %>%
  group_by(sex) %>%
  summarise(total = sum(count))
```



```{r}
# data(BabyNames, package = "DataComputing")
BabyNames %>%
  filter(grepl("kk", name)) %>%
  summarise(total = sum(count))
```



##### any pair of letters followed by a pair of the same letters
```{r}
# data(BabyNames)
BabyNames %>%
  filter(grepl("(aa|bb|cc|dd|ee|ff|gg|hh|ii|jj|kk|ll|mm|nn|oo|pp|qq|rr|ss|tt|uu|vv|ww|xx|yy|zz){2,}", name)) %>% head
```


```{r}
BabyNames %>%
  filter(grepl("(aa|bb|cc|dd|ee|ff|gg|hh|ii|jj|kk|ll|mm|nn|oo|pp|qq|rr|ss|tt|uu|vv|ww|xx|yy|zz){3,}", name)) %>% head
```


```{r}
BabyNames %>%
  filter(grepl("(aa|bb|cc|dd|ee|ff|gg|hh|ii|jj|kk|ll|mm|nn|oo|pp|qq|rr|ss|tt|uu|vv|ww|xx|yy|zz){3,}", name)) %>% 
  summarise(total = n())
```


##### ends with 3 vowels
```{r}
BabyNames %>%
  filter(grepl("[aeiouy]{3}$", name)) %>% head
```



```{r}
BabyNames %>%
  filter(grepl("[aeiouy]{4}$", name)) %>% 
  summarise(total = n())
```



* $ = in the end
* | = or


```{r}
str_view_all(BabyNames, "aa")
str_view_all(BabyNames$name, "L.*") # anything starting with L
str_view_all(BabyNames$name, "[LD].*") # anything starting with L or D
```



# To KNOW:

^, $, 



### FROM THE BOOK
#### Examples of Graphs

```{r warning = FALSE}
CPS85 %>%
ggplot(aes(x=wage)) +
geom_density(aes(fill=sex,color=sex), alpha=0.5) +
facet_grid( . ~ married) +
ggtitle("(A)") + xlim(0,30)
```

```{r warning = FALSE}
CPS85 %>%
ggplot(aes(x=age, y=wage)) +
geom_smooth(aes(color=sex)) +
ggtitle("(B)") +
facet_grid( married ~ .) + ylim(0,NA)
```

```{r warning = FALSE}
CPS85 %>%
ggplot(aes(x=age, y=wage)) +
ggtitle("(C)") +
geom_smooth(aes(color=sex)) +
facet_wrap( ~ sector) + ylim(0,25)
```

```{r warning = FALSE}
mosaicData::CPS85 %>%
ggplot(aes(x = educ, y = wage,
color = sex)) +
geom_point() +
stat_smooth(method="lm") +
ylim(0,15)
```

```{r warning = FALSE}
mosaicData::Galton %>%
ggplot(aes(x = height, y = mother)) +
geom_density2d() +
facet_grid( ~ sex)
```


















