# **Week 2 Short Answer Questions**

## Yunjae Choi

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
<!-- put your content after this line -->

&nbsp;    
&nbsp;    

### Chapter 1
    
##### Problem 1.1

a. 3
b. 2
c. 1
d. 1
e. 2

&nbsp;    

##### Problem 1.2

    The table is not "tidy" in that the cases within each of the variables are not in the same format. They have to be in a uniform format in order for R to do operations on our commands. For example, all names can be in one form: "Last name, First name," or "First name Last name," but not both.

&nbsp;    

##### Problem 1.4

1. What are the variables in each table?

    * Data Table A: Year, Algeria, Brazil, Columbia
    * Data Table B: Country, Y2000, Y2001
    * Data Table C: Country, Year, Value
      
&nbsp;    

2. What is the meaning of a case for each table?

    * Data Table A: A year
    * Data Table B: A country
    * Data Table C: A country in a year

&nbsp;    

##### Problem 1.5

1. How many variables are there? 
        
        8
        
2. What do the cases represent? 

        Airport names in FAA airport code
      
3. For each variable, make a reasonable guess about whether the values will be numerical or quantitative.

        * faa - categorical
        * name - categorical
        * lat - quantitative
        * lon - quantitative
        * alt - quantitative
        * tz - quantitative
        * dst - categorical
        * tzone - categorical
        
&nbsp;    

##### Problem 2.2

    file name

&nbsp;    

##### Problem 2.3
```{r}
# install.packages("mosaicData")
# data(data = CPS85, package = "mosaicData")
# help(CPS85, package = "mosaicData")
```

        The Current Population Survey (CPS) is used to supplement census information between census years. These data consist of a random sample of persons from the CPS85, with information on wages and other characteristics of the workers, including sex, number of years of education, years of work experience, occupational status, region of residence and union membership.

&nbsp;    

##### Problem 2.4

        the data name cannot be the same as the package name. A package contains a number of data. The package here should be where NHANES comes from.

&nbsp;    

##### Problem 2.6

1. OK
2. Wrong

        a dash (-) is not one of the allowed punctuation marks in an object name.

3. Wrong
  
        Being in quotes, "MyData" is a constant, not an object name.

4. OK
5. Wrong

        a space is not allowed in an object name
    
6. OK
7. OK
8. OK


9. Wrong

        parentheses not allowed 

&nbsp;    

##### Problem 2.7

Installing done above.
```{r}
data(flights, package = "nycflights13")
```

1. How many variables are there? 
```{r}
ncol(flights)
```

2. How many cases are there? 
```{r}
nrow(flights)
```

3. What is the meaning of a case? ("Meaning" refers to the kind of entity, for instance, "airport" or "airline" or "date". Hint: the case in flights is not any of these things.) 
On-time data for all flights that departed NYC (i.e. JFK, LGA or EWR) in 2013.

        To look up the meanings of variables:
    
```{r}
# Help(flights)
```

4. For each variable, is the variable quantitative or categorical?
```{r}
str(flights)
class(flights$time_hour) # this can be considered a string
```

5. For the variables air_time and distance, what are the units?     

        minutes
        
```{r}
# Help(flights)
```

&nbsp;    

##### Problem 2.8

"<--" indicates to what it should be changed.

a. ralph <- sqrt 10               

        3
    
b. ralph2 <-- "Hello to you!"     
    
        1
    
c. 3ralph <- "Hello to you!"      

        4
    
d. ralph4 <- "Hello to you!       

        2
    
e. ralph5 <- date()               

        5
    
&nbsp;    

##### Problem 2.9

1. "." and "_"
2. All of them


&nbsp;    

##### Problem 2.10

1.
```{r}
data(data = CountryData, package = "DataComputing")
ncol(CountryData)
```

2. mass of trunk fat
```{r}
# help(NCHS, package = "DataComputing")
```

3.
```{r}
data(data = WorldCities, package = "DataComputing")
nrow(WorldCities)
```

4. Count
```{r}
data(data = BabyNames, package = "DataComputing")
head(BabyNames)
```

5. 
```{r}
data(RegisteredVoters, package = "DataComputing")
levels(RegisteredVoters$party)
```


&nbsp;    

##### Problem 3.1

1. data frame (fireplace)

    Put it at the start of a chain, e.g. fireplace %>% nrow()
```{r}
fireplace <- data.frame(c(1,2,3,4,5), row.names = 1,4,36)
fireplace
```

&nbsp;    

2. a function (b)

    In this case, "sqrt" is a function; Follow it by an open parenthesis, fileplace(

&nbsp;    

3. the name of a named argument (c)

    "BabyNames" is the name of a named argument, "data"; Follow it by = inside the parentheses of a function, e.g., fun(fileplace = 7)

&nbsp;    

4. a variable (d)

    "sex" in "BabyNames"; place it inside the parentheses of a function, but not in the position of the name of a named argument, e.g., fun(fileplace) or fun(x = fireplace)

&nbsp;    

##### Problem 3.2

    "Result <- %>% filter(BabyNames, name=="Prince")" is illegitimate because there's no data frame that the filter function is being applied to. It should be
```{r}
library("magrittr")
Result <- 
  BabyNames %>% 
  filter(name == "Prince")
```

&nbsp;    

##### Problem 3.3

    A package contains many data set. Therefore, NHANES cannot be the package for this particular data set, "NHANES"
```{r}
# help(NHANES, package <- "NHANES")
```

&nbsp;    

##### Problem 3.4

```{r}
# BabyNames = data(data = BabyNames, package = "DataComputing")

Princes <-
  BabyNames %>%
  filter(name == "Prince") %>%
  group_by(year, sex) %>%
  summarise(yearlyTotal = sum(count))

# Now graph it!
Princes %>%
  ggplot(aes(x = year, y = yearlyTotal)) +
  geom_point(aes(color = sex)) +
  geom_vline(xintercept = 1978)
```

1. b
2. a
3. c
4. a
5. a
6. c
7. c
8. a
9. d
10. a
11. c?
12. a
13. a
14. c
15. c
16. a
17. d
18. a
19. d


&nbsp;    

##### Problem 3.5

```{r}
data(msleep, package = "ggplot2")
# help(msleep)
nrow(msleep)
```

1. brainwt. brain weight in kilograms
2. 83
3. number of observations in the data
4. carnivore, omnivore or herbivore

&nbsp;    

##### Problem 3.6

    Statement (c) is different. Rather than calculating the total number of births (using sum()), it finds the mean number of births across all the cases in each year/sex group.

&nbsp;    
&nbsp;    

### Chapter 4

&nbsp;    

##### Problem 4.1

1. italics: *one*
2. bold face: **two**
3. bullet point:

        * three

4. biggest size of the headings 

# Four

5. it would just print out 'five'

`five`

6. "Six" that is of a smaller size than the biggest size "#"

## Six

7. text "seven" that takes us to the following link

[seven](http://tiny.cc/dcf/index.html)


&nbsp;    

##### Problem 4.2

1. not correct "`" mark
1. not correct "`" mark
1. need 3 "`" marks each in the beginnning and end
1. need parallel marks (in two lines)
1. need 3 "`" marks each in the beginnning and end


&nbsp;    

##### Problem 4.3

### An Introduction

Arithmetic is *easy*! For instance
```{r}
3 + 2
```

The above heading will be in bigger font than the rest. The text "easy" will be italicized. 3 + 2 will appear in the calculated form 5.

&nbsp;    

##### Problem 4.4

1. a possible URL
1. a possible file
1. neither
1. a possible URL
1. neither
1. a possible file


&nbsp;    

##### Problem 4.5

Done on a separate file Birds.Rmd
