# **Week 4 Short Answer Questions**

## Yunjae Choi

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
```
<!-- put your content after this line -->

&nbsp;    
&nbsp;    

### Chapter 8
    
##### Problem 8.1


a) geom_point() 

    (2) Add a layer of glyphs
    
&nbsp;    

b) geom_histogram() 

    (2) Add a layer of glyphs
    
&nbsp;    

c) ggplot() 

    (1) Construct the graphics frame
    
&nbsp;    

d) scale_y_log10()

    (5) Change the scale for the frame.
    
&nbsp;    

e) ylab() 

    (3) Set an axis label
    
&nbsp;    

f) facet_wrap()

    (4) Divide the frame into facets
    
&nbsp;    

g) geom_segment() 

    (2) Add a layer of glyphs
    
&nbsp;    

h) xlim()

    (5) Change the scale for the frame.
    
&nbsp;    

i) facet_grid()

    (2) Add a layer of glyphs
    
&nbsp;    

##### Problem 8.2

```{r, echo=TRUE}
data(CPS85, package = "mosaicData")
names(CPS85)
str(CPS85$sector)
sectornum <- as.numeric(CPS85$sector)
```

```{r}
ggplot(data = CPS85, aes(x = age, y = wage, shape = married)) +
  geom_point() +
  facet_wrap(~CPS85$sector, nrow = 3)
```

```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage)) +
  geom_point() +
  facet_grid(CPS85$sex ~ CPS85$married)
```


&nbsp;    

##### Problem 8.3

a.
```{r}
CPS85 %>%
  ggplot(aes(age, wage)) +
  geom_point()
```

b.

error in the book:

```{r}
HappinessIndex %>%
  WorldMap(key="country", fill="corruption")
```


c.
```{r}
ggplot(data = CPS85, aes(x = age, y = wage)) +
  geom_point(aes(shape = sex)) +
  facet_grid( married ~ .) 
```

d.
```{r}
CPS85 %>%
  ggplot(aes(x = age, y = wage)) +
  geom_point(aes(shape = married)) +
  ylim(0,30)
```

&nbsp;    
&nbsp;    

### Chapter 9

##### Problem 9.1

* str() - Quick presentation
* group_by() - Data verb
* rank() - Transformation
* mean() - Summary Function
* filter() - Data Verb
* summary() - Quick presentation
* summarise() - Data verb
* merge() - Data verb
* glimpse() - Quick presentation

&nbsp;    

##### Problem 9.3

1. 
```{r}
diamonds %>%
  group_by( color ) %>%
  summarise( largAve = mean(carat, na.rm = TRUE) ) %>%
  arrange(desc( largAve )) %>%
  head( 1 )
```


2. 
```{r}
diamonds %>%
  group_by( clarity ) %>%
  summarise( largAveTable = mean(table, na.rm = TRUE) ) %>%
  arrange(desc( largAveTable )) %>%
  head( 1 )
```












