---
title: '**Week 5: In Class Notes**'
author: "Yunjae Choi"
date: "March 15, 2017"
output: html_document
---

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(dplyr)
```
<!-- put your content after this line -->

&nbsp;
&nbsp;

### OrdwayBirds - `left_join`, `gather`, `tally`
```{r}
data(OrdwayBirds, package = "DataComputing")
load("~/Comp-110-Assignments-Spring-2017/Data Sets/Birds_cleaningData.Rda")
```

&nbsp;

##### Assign a Different Name
```{r}
Birds <- OrdwayBirds
```

&nbsp;

##### `left_join`
```{r}
Birds %>% 
  left_join(Cleaned_species)
```

&nbsp;

##### `left_join` and `group_by` + `tally`
```{r}
Birds %>% 
  left_join(Cleaned_species) %>% 
  group_by(SpeciesNameCleaned) %>%
  tally() 
```

&nbsp;

##### `left_join` and `group_by` + `tally` and `arrange(desc(n))`

```{r}
Birds %>% 
  left_join(Cleaned_species) %>% 
  group_by(SpeciesNameCleaned) %>%
  tally() %>%
  arrange(desc(n))
```

&nbsp;

##### Preparing Cleaned_species Data Set
```{r}
# Cleaned_species <- read.csv(file.choose(), stringsAsFactors = FALSE)
# View(Cleaned_species)
```

```{r}
load("C:\\Users\\Diana Choi\\Documents\\Comp-110-Assignments-Spring-2017\\Data Sets\\Library-small.rda")
Cleaned_species <- Cleaned_species %>% select(-X)
save(Cleaned_species, file = "Class_cleaning_data.Rda")
View(Birds)
```

&nbsp;

#### _Summary of Important Functions_

##### `left_join`

return all rows from x, and all columns from x and y. Rows in x with no match in y will have NA values in the new columns. If there are multiple matches between x and y, all combinations of the matches are returned (x and y are tables to join).

        left_join(x, y, by = NULL, copy = FALSE, suffix = c(".x", ".y"), ...)

```{r}
foo <- Birds %>% 
  left_join(Cleaned_species, by = c(SpeciesName = "SpeciesName"))
```

&nbsp;

##### `spread`

* Spread a key-value pair across multiple columns.
* narrow -> wide (whereas `gather` is wide -> narrow)

        spread(data, key, value, fill = NA, convert = FALSE, drop = TRUE, sep = NULL)

```{r}
ByName <- BabyNames %>% 
  group_by(name, sex) %>% 
  summarise(total = sum(count))
nrow(BabyNames)
head(ByName)
```

```{r}
BySex <- ByName %>% 
  tidyr::spread(key = sex, total)
head(BySex)
```

&nbsp;

#### _Some More Practice_

1. 
```{r}
BySex <- BySex %>%
  filter(F>1000, M>1000)
head(BySex)
```

2.
```{r}
BySex <- BySex %>%
  mutate(ratio = F/M)
head(BySex)
```

&nbsp;

#### _Some More Practice with Graphing_

1. 
```{r}
ggplot(BySex, aes(x = ratio)) + geom_density()
```

2. 
```{r}
ggplot(BySex, aes(x = log(ratio))) + geom_density()
```




